\documentclass[]{article} %la classe mi preimposta alcune opzioni 
\usepackage{subfiles}
%latex packages
%
% ------------------PACKAGES
% 
\usepackage{graphicx} %per inserire figure
\usepackage{enumerate} %per liste numerate, mettere * quando non voglio il nr
\usepackage{wrapfig} % raggruppare una figura e poterne gestire meglio il posizionamento
\usepackage{comment} % mi permette di commentare più linee
\usepackage{csquotes} %for quotations
\usepackage{blindtext} %for random text

\usepackage{tikz} % for drawing lines
%\newtheorem{definition}{printed def} % può essere utile per le definizioni
%\newtheorem*{remark}{nota}
\usepackage{lmodern} %in alternativa lmodern, palatino, times, helvet
\usepackage[dvipsnames]{xcolor} %per una gestioen più ampia dei colori, lopzione tra [] mi da più ampia scelta di colori find other colors here https://www.overleaf.com/learn/latex/Using_colors_in_LaTeX
%\usepackage[scaled]{beramono} %resets the monospace font in the document
\usepackage{dialogue} % per i dialoghi
\usepackage{fancybox} %per caselle di testo

\definecolor{MyCustomColor}{RGB}{198,162,1}
\definecolor{NewColor}{HTML}{665544}
%
\usepackage{multicol} % Essential for multi-column layouts

% Other useful packages (explained later)
\usepackage{lipsum}  % For generating filler text
\usepackage[margin=0.75in, a4paper]{geometry} % To control page margins
\usepackage{fancyhdr} % For custom headers/footers
\usepackage{exsheets} %for exercises 
\pagestyle{fancy}


\lhead{Lesson 3 - Ist. Mandes - Casalvecchio}
\rhead{My Day}   % Right header content
\rfoot{14/05/2024}% lesson 4 casalnuovo


% lesson 5 

\begin{document}
	
\subsection{Action: The picnic basket}

Characters:\\
\\
Narrator: Guides the story and asks questions to the audience.\\
\\
Picnic Group:\\
The Leader: Energetic and enthusiastic.\\
The Hungry One: Always focused on food.\\
The Lost One: Easily distracted and prone to wandering off.\\
The Helper: Always ready to lend a hand.\\
The Worrier: Concerned about everything.\\
The Others: (5 additional characters) Can have various personalities to add humor or variety.\\
Scene: A park or forest clearing. A large, colorful picnic blanket is spread out, but it's empty.\\
\\
\iffalse\\
Props (Optional):\\
\\
A large, empty picnic basket\\
Pictures or drawings of food items (fruits, sandwiches, etc.)\\
Signs with simple directions (e.g., "This way," "That way")\\
A map (very basic)\\
Sketch:\\
\fi\\
\\
Introduction: The Narrator sets the scene. The Picnic Group enters, looking excited. They notice their picnic basket is missing.\\
Vocabulary Practice:\\
Leader: "Oh no! Where is our food?" (Points to their stomachs and makes a sad face)\\
Group: (Together) "Hungry!"\\
Helper: "Let's look around! Maybe it's close."\\
Narrator: (To the audience) "What do we call the things we eat at a picnic?"\\
Audience: (Hopefully) "Food!"\\
Search Begins: The Group spreads out, using simple English phrases like "I see a tree," "Is it under there?" They find clues:\\
A piece of fruit (apple, banana, etc.)\\
A napkin\\
Footprints\\
Narrator: (Each time a clue is found) "What did they find?" (Holds up a picture of the item)\\
Encountering Obstacles:\\
Lost One: (Walks in a circle, confused) "Where am I?"\\
Worrier: "Oh dear! What if we never find it?"\\
Leader: "Don't worry! We'll find it together!"\\
Narrator: (To audience) "What do we say when we're scared or worried?"\\
Audience: (Hopefully) "Help!" or "Scared!"\\
Discovery: The group follows the clues and eventually finds the picnic basket hidden behind a tree or bush.\\
Hungry One: "Hooray! Food!"\\
Group: (Cheers and claps)\\
Celebration: They enjoy their picnic, using simple phrases to describe the food: "Yummy," "Sweet," "Delicious," "Good!"\\

\iffalse
Additional Notes:
Flexibility: Encourage improvisation and adapt the sketch to your students' specific vocabulary level.
Repetition: Repeat key words and phrases throughout the sketch.
Visual Aids: Use props and gestures to reinforce vocabulary.
Engagement: Ask the audience questions and encourage them to participate in the story.
\fi

\subsection{Listening: daily routine}
https://www.youtube.com/watch?v=L31ExXwlsVc 

\subsubsection*{Answer the following questions}
\begin{enumerate}
	\item What time does the speaker wake up in the morning?
\item What does the speaker usually have for breakfast?
\item When does the speaker start working and finish working?
\item Where does the speaker usually go for lunch?
\item What is the speaker currently studying at the University?
\item What does the speaker do after classes in the evening?
\item What time does the speaker usually go to bed?
\end{enumerate}

\iffalse 
The speaker wakes up at eight o'clock in the morning.
2
The speaker usually has avocado toast and a coffee with milk for breakfast.
3
The speaker starts working at half-past nine and finishes working at 2:00 p.m.
4
The speaker usually goes to the cafeteria for lunch or an Italian restaurant for pizza.
5
The speaker is currently earning a master's degree in English studies.
6
After classes, the speaker either goes to the gym or goes out with friends.
7
The speaker falls asleep at midnight.
\fi 


\subsection*{Daily routine}
Listen to the text and unscramble the sentences. 

\iffalse 
% parte per il docente
Hi everyone! I'm an English student, and I'm going to tell you about my daily routine. Every day is a little different, but here's what I usually do.

In the morning, I wake up around 7 o'clock. I get dressed, have breakfast, and then I start studying. I usually spend about an hour reviewing grammar and vocabulary, and then I do some reading or listening practice. I also try to speak English with my classmates or online friends whenever I can.

In the afternoon, I have my English class. I always look forward to this part of my day because I get to learn new things and practice speaking with my classmates and teacher. After class, I often go to the library or a café to do some more studying or homework.

In the evening, I like to relax and have some fun. I might watch a movie in English, listen to music, or read a book. I also try to get to bed early so I can be well-rested for the next day.

On weekends, I have more free time, so I often do activities that help me improve my English. I might go to a language exchange event, watch a movie in English with subtitles, or even try to cook a recipe in English!

\subsubsection*{unscramble the words}
\fi 
\begin{enumerate}
	\item daily / tell / about / you / student / to / my / I'm / going / I'm / routine / English / an / and\\
	\item I / little / what / a / usually / day / is / different / but / Every / here's / do\\
	\item 7 / wake / morning / up / I / o'clock / around / In / the\\
	\item I / breakfast / get / start / and / then / I / studying / dressed / have\\
	\item do / some / reviewing / listening / vocabulary / about / spend / and / practice / an / hour / or / reading / then / usually / and / I / I / grammar\\
	\item speak / online / whenever / I / I / friends / can / or / with / classmates / English / my / try / to / also\\
	\item class / In / afternoon / I / have / my / the / English\\
	\item I / because / classmates / to / to / I / and / forward / day / new / of / my / teacher / things / part / look / this / speaking / with / get / and / always / my / practice / learn\\
	\item more / some / go / library / often / café / homework / I / to / do / a / to / the / class / After / studying / or / or\\
	\item evening / to / some / relax / fun / like / have / I / In / and / the\\
	\item English / to / I / listen / read / in / watch / or / movie / music / might / a / a / book\\
	\item try / so / day / the / get / to / well-rested / I / for / I / be / also / can / to / early / bed / next\\
	\item improve / help / On / do / have / time / my / free / that / me / I / weekends / so / activities / English / more / I / often\\
	\item to / to / a / might / movie / in / a / with / subtitles / language / I / recipe / watch / even / exchange / cook / or / in / English / English / event / go / a / try\\
\end{enumerate}
	\subsection{Reading and comprehension}
	
	\subsubsection*{Let's introduce Emma}
	
My friend's name is Emma. She's a student and she's 21 years old. She has lots of friends because she's very friendly and she always makes people laugh. Emma loves going out with her friends at the weekend and dancing in clubs, but she doesn't like noisy parties at home. She's quite tall and slim. She has long straight brown hair and big green eyes. She usually wears jeans and a T-shirt or a dress. Emma's from London, but she lives in a student house in Manchester during term time. She studies English Literature at Manchester University and she wants to be a writer one day. Emma also loves travelling. She's been to France, Spain, Italy and Greece. Last summer she went to Australia and she stayed with some friends in Melbourne for three months. She loved it! Emma's very intelligent and she works hard at university, but she doesn't study all the time. She often goes to the cinema or reads books in the park when it's sunny. Her favourite author is Jane Austen and her favourite film is The Shawshank Redemption. Emma's really nice and she's a great friend. I see her every day at college and we have lunch together. We sometimes go shopping after college or go to the cinema at the weekend. We're both busy, but we always make time for each other.
	
	
	\subsubsection*{Questions}
	
	\begin{enumerate}
\item What is Emma's occupation?\\
\item Where does Emma live during the term time?\\
\item Which countries has Emma visited?\\
\item What is Emma studying at Manchester University?\\
\item What does Emma do in her free time when it's sunny?\\
\item Who is Emma's favorite author?\\
\item How often do the author and Emma see each other?\\
	\end{enumerate}
	
	
\subsection*{match the halves}
\begin{tabular}{l r}
My favourite thing to do is have & a the papers in the morning with my\\
Cycling & is one of my favourite forms of exercise.\\
Every morning is breakfast & presents for my loved ones.\\
In the mornings, I listen to & good mood.\\
One of my favourite things to do is & the radio while getting ready for the day.\\
After a long day, I can't wait to get home & cup of tea.\\
Whenever I am listening to music, I am & time and my favourite meal of the day.\\
I always have a & big breakfast to start my day off right.\\
On a public holiday, I usually sleep in & a lazy day.\\
I like to read & from work.\\
\end{tabular}

\subsection{dialogues}
	Chose 4 questions and discuss with your classmate
	\begin{itemize}
		\item 	What do you like to do when you get home from work?\\
		\item 	Do you have a favorite breakfast time?\\
		\item 	Do you usually have a big breakfast in the morning?4 What do you like to have for breakfast?\\
		\item Do you like to read the papers in the morning?\\
		\item Do you listen to the radio while getting ready for your day?\\
		\item Have you ever tried cycling as a form of exercise?\\
		\item Do you enjoy public holidays?\\
		\item Do you like buying presents for others?\\
		\item Are you usually in a good mood in the morning?\\
	\end{itemize}
\end{document}
