\documentclass[]{article} %la classe mi preimposta alcune opzioni 
\usepackage{subfiles}
%latex packages
%
% ------------------PACKAGES
% 
\usepackage{graphicx} %per inserire figure
\usepackage{enumerate} %per liste numerate, mettere * quando non voglio il nr
\usepackage{wrapfig} % raggruppare una figura e poterne gestire meglio il posizionamento
\usepackage{comment} % mi permette di commentare più linee
\usepackage{csquotes} %for quotations
\usepackage{blindtext} %for random text

\usepackage{tikz} % for drawing lines
%\newtheorem{definition}{printed def} % può essere utile per le definizioni
%\newtheorem*{remark}{nota}
\usepackage{lmodern} %in alternativa lmodern, palatino, times, helvet
\usepackage[dvipsnames]{xcolor} %per una gestioen più ampia dei colori, lopzione tra [] mi da più ampia scelta di colori find other colors here https://www.overleaf.com/learn/latex/Using_colors_in_LaTeX
%\usepackage[scaled]{beramono} %resets the monospace font in the document
\usepackage{dialogue} % per i dialoghi
\usepackage{fancybox} %per caselle di testo

\definecolor{MyCustomColor}{RGB}{198,162,1}
\definecolor{NewColor}{HTML}{665544}
%
\usepackage{multicol} % Essential for multi-column layouts

% Other useful packages (explained later)
\usepackage{lipsum}  % For generating filler text
\usepackage[margin=0.75in, a4paper]{geometry} % To control page margins
\usepackage{fancyhdr} % For custom headers/footers
\usepackage{exsheets} %for exercises 
\pagestyle{fancy}


%\lhead{Lesson 3 - Ist. Mandes - Casalvecchio}
%\rhead{My Day}   % Right header content
%\rfoot{14/05/2024}% lesson 4 casalnuovo


% lesson 5 

\begin{document}
\subsection {speaking and listening} 
game: one person makes a statement, then "pass the ball" to the next who says: 
I agree, I disagree, I don't agree. Then makes another statement.

\begin{itemize}

\item Video games are more fun than playing outside.
It's okay to sometimes break the rules.
Homework is the best way to learn.
Everyone should have a pet.
Money is more important than happiness.
The best way to make friends is online.
Robots will take over the world one day.
It's better to be popular than to be kind.
School uniforms should be mandatory everywhere.
Summer vacation should be longer than winter vacation.
\end{itemize}

\subsection*{Sentence creation}
Make 5 sentences by using at least 1 item of each group per sentence

\begin{longtable}{| l | l | l | l |}
	\hline
	Nouns & Verbs & Adjectives & Adverbs \\

friend - 
family - 
house - 
school - 
book - 
game - 
food - 
music - 
movie - 
phone - 

	& 
play - 
eat - 
sleep - 
go - 
like - 
love - 
want - 
need - 
think - 
know - 
be - 
have - 
do - 
say - 
get - 
make - 
go - 
know - 
take - 
see - 
come - 
think - 
look - 
want - 
give - 
use - 
find - 
tell - 
ask - 
work - 
seem - 
feel - 
try - 
leave - 
call - 
help - 
talk - 
hear - 
play - 
run - 
 - 
	&  
good - 
bad - 
happy - 
sad - 
big - 
small - 
new - 
old - 
young - 
hot - 
cold - 
long - 
short - 
fast - 
slow - 
high - 
low - 
right - 
wrong - 
easy - 
hard - 
different - 
same - 
beautiful - 
ugly - 
interesting - 
boring - 
funny - 
serious - 
important - 
 - 
&   
 - 
always - 
never - 
sometimes - 
often - 
very - 
really - 
quickly - 
slowly - 
well - 
badly \\
\end{longtable}

\end{document}
